The Forecast Trap

### 2021-09-17 manuscript/manuscript.Rmd
:robot:
caps
trigger Rmd build
update abstract

---
title: "The forecast trap"
name: Carl Boettiger
email: "cboettig@berkeley.edu"
affiliation: a,1
date: "`r Sys.Date()`"

abstract: |
  Encouraged by decision makers' appetite for future information on topics ranging from elections to pandemics, and enabled by the explosion of data and computational methods, model based forecasts have garnered increasing influence on a breadth of decisions in modern society. Using a classic example from fisheries management, I demonstrate that selecting the model or models that produce the most accurate and precise forecast (as measured by most widely used statistical scores) can lead to decidedly worse outcomes (as measured by real-world objectives such as dollars or fish). This can create a forecast trap: in which the manager not only over-exploits the fishery leading to declining biomass and declining yields, but also becomes increasingly convinced that these actions are not over-exploitation but in fact consistent with the best models and data for sustainable management. The forecast trap is not unique to this example, but possible whenever (1) the optimal management policy is not unique to the generative process, and (2) the generative process is not itself in our candidate set of models.

>>>>

---
title: "The Forecast Trap"
name: Carl Boettiger
email: "cboettig@berkeley.edu"
affiliation: a,1
date: "`r Sys.Date()`"

abstract: |
  Encouraged by decision makers' appetite for future information on topics ranging from elections to pandemics, and enabled by the explosion of data and computational methods, model based forecasts have garnered increasing influence on a breadth of decisions in modern society. Using a classic example from fisheries management, I demonstrate that selecting the model or models that produce the most accurate and precise forecast (measured by statistical scores) can lead to decidedly worse outcomes (measured by real-world objectives). This can create a forecast trap, in which the outcomes such as fish biomass or economic yield decline while the manager becomes increasingly convinced that these actions are consistent with the best models and data available. The forecast trap is not unique to this example, but possible whenever (1) the optimal management policy is not unique to the generative process, and (2) the generative process is not in our candidate set of models.
